% Formal Business Letter Template
% Compile: pdflatex letter.tex (single pass)
\documentclass[11pt,a4paper]{letter}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage[margin=1in,top=1.2in]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{colorlinks=true,urlcolor=blue}

% Customize signature space
\longindentation=0pt

% ============================
% SENDER INFO
% ============================
\name{Jane Mitchell}
\address{
    \textbf{Jane Mitchell}\\
    Chief Technology Officer\\
    Acme Corp\\
    123 Innovation Drive, Suite 800\\
    San Francisco, CA 94102\\
    \href{mailto:jane.mitchell@acmecorp.com}{jane.mitchell@acmecorp.com}\\
    +1 (555) 987-6543
}

% Date
\date{March 22, 2026}

% Signature
\signature{Jane Mitchell\\Chief Technology Officer\\Acme Corp}

\begin{document}

\begin{letter}{
    Mr. David Chen\\
    Vice President of Engineering\\
    TechPartner Inc.\\
    456 Enterprise Boulevard\\
    Austin, TX 78701
}

\opening{Dear Mr. Chen,}

Thank you for taking the time to meet with our team last Thursday to discuss the potential technology partnership between Acme Corp and TechPartner Inc. We were impressed by your platform's capabilities and see significant alignment between our organizations.

Following our discussion, I wanted to outline the key areas where we believe a partnership would create mutual value:

\textbf{Integration Opportunities.} Your data processing pipeline complements our analytics platform. By building a native integration, we could offer our combined customer base a seamless workflow that neither company can deliver independently. Based on our initial analysis, this could address a \$12M market opportunity.

\textbf{Joint Go-to-Market.} Several of our Enterprise customers have expressed interest in the exact capabilities your platform provides. We propose a co-selling arrangement where our sales teams collaborate on accounts that fit the combined solution profile. Our preliminary list includes 15 accounts with a combined pipeline value of \$4.2M.

\textbf{Technical Collaboration.} Our engineering teams could benefit from a shared knowledge exchange, particularly around your real-time processing architecture and our experience with large-scale distributed systems.

As next steps, I propose we schedule a working session between our technical leads to scope the integration effort and draft a partnership framework. My team is available the week of April 7 and could host at our San Francisco office, or we're happy to travel to Austin.

Please let me know if this aligns with your thinking and whether you'd like to adjust the scope or timeline. I've asked our VP of Partnerships, Sarah Kim (\href{mailto:sarah.kim@acmecorp.com}{sarah.kim@acmecorp.com}), to coordinate scheduling once we have your confirmation.

We're excited about the potential here and look forward to building something great together.

\closing{Warm regards,}

\encl{Partnership Framework Draft (v0.1)\\NDA for mutual execution}
\cc{Sarah Kim, VP of Partnerships\\Mark Torres, Head of Engineering}

\end{letter}
\end{document}
